Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-19 paper.qmd
Updated the true model

To illustrate the method, we use $7\text{-}D$ simulated data, which we call the "non-linear clusters". It is constructed by simulating $n=2000$ observations from $\theta \sim U(-3\pi/2, 0)$, $X_1 = \sin(\theta)$, $X_2 \sim U(0, 2)$ (adding thickness to the C), $X_3 = \text{sign}(\theta) \times (\cos(\theta) - 1)$. The remaining variables $X_4, X_5, X_6, X_7$ are all uniform error, with small variance. We would consider $T=(X_1, X_2, X_3)$ to be the geometric structure (true model) that we hope to capture.

>>>>

To illustrate the method, we use $7\text{-}D$ simulated data, which we call the "non-linear clusters". It is constructed by simulating two clusters, each consisting of $1000$ observations. The C-shaped cluster is generated from $\theta \sim U(-3\pi/2, 0)$, $X_1 = \sin(\theta)$, $X_2 \sim U(0, 2)$ (adding thickness to the C), $X_3 = \text{sign}(\theta) \times (\cos(\theta) - 1)$. The other cluster is from $X_1 \sim U(0, 2)$, $X_2 \sim U(0, 3)$, $\gamma \sim U(0, 0.5)$, and $X_3 = -(X_1^3 + X_2) + \gamma$.

The remaining variables $X_4, X_5, X_6, X_7$ are all uniform error, with small variance. We would consider $T=(X_1, X_2, X_3)$ to be the geometric structure (true model) that we hope to capture.
